Millions of Americans and foreigners see G.I. Joe as a mindless war toy, the symbol of American military adventurism, but that's not how it used to be. To the men and women who \uline{~~1~~} in World War \uppercase\expandafter{\romannumeral2} and the people they liberated, the G.I. was the \uline{~~2~~} man grown into hero, the poor farm kid torn away from his home, the guy who \uline{~~3~~} all the burdens of battle, who slept in cold foxholes, who went without the \uline{~~4~~} of food and shelter, who stuck it out and drove back the Nazi reign of murder. This was not a volunteer soldier, not someone well paid, \uline{~~5~~} an average guy, up \uline{~~6~~} the best trained, best equipped, fiercest, most brutal enemies seen in centuries.


His name isn't much. G.I. is just a military abbreviation \uline{~~7~~} Government Issue, and it was on all of the articles \uline{~~8~~} to soldiers. And Joe? A common name for a guy who never \uline{~~9~~} it to the top. Joe Blow, Joe Palooka, Joe Magrac... a working class name. The United States has \uline{~~10~~} had a president or vice-president or secretary of state Joe.


G.I. Joe had a \uline{~~11~~} career fighting German, Japanese, and Korean troops. He appears as a character, or a \uline{~~12~~} of American personalities, in the 1945 movie The Story of G.I. Joe, based on the last days of war correspondent Ernie Pyle. Some of the soldiers Pyle \uline{~~13~~} portrayed themselves in the film. Pyle was famous for covering the \uline{~~14~~} side of the war, writing about the dirt-snow-and-mud soldiers, not how many miles were \uline{~~15~~} or what towns were captured or liberated. His reports \uline{~~16~~} the ``Willie'' cartoons of famed Stars and Stripes artist Bill Maulden. Boh men \uline{~~17~~} the dirt and exhaustion of war, the \uline{~~18~~} of civilization that the soldiers shared with each other and the civilians: coffee, tobacco, whiskey, shelter, sleep. \uline{~~19~~} Egypt, France, and a dozen more countries, G.I. Joe was any American soldier, \uline{~~20~~} the most important person in their lives.