Harlan Coben believes that if you're a writer, you'll find the time; and that if you can'tfind the time, then writing isn't a priority and you're not a writer. For him, writing is a \uline{~~1~~} job — a job like any other. He has \uline{~~2~~} it with plumbing, pointing out that a plumberdoesn't wake up and say that he can't work with pipes today.


\uline{~~3~~} , like most writers these days, you're holding down a job to pay the bills, it's not \uline{~~4~~} to find the time to write. But it' s not impossible. It requires determination and singlemindedness. \uline{~~5~~} that most bestselling authors began writing when they were doingother things to earn a living. And today, even writers who are fairly \uline{~~6~~} often have todo other work to \uline{~~7~~} their writing income.


As Harlan Coben has suggested, it's a \uline{~~8~~} of priorities. To make writing a priority,you'll have to \uline{~~9~~} Some of your day-to-day activities and some things you really enjoy. Depending on your \uline{~~10~~} and your lifestyle, that might mean spending less timewatching television or listening to music, though some people can write \uline{~~11~~} they listento music. You might have to \uline{~~12~~} the amount of exercise or sport you do. You'll haveto make social media an \uline{~~13~~} activity rather than a daily, time-consuming \uline{~~14~~} . There'll probably have to be less socialising with your friends and less time with your family. It's a \uline{~~15~~} learning curve and it won't always make you popular.


There's just one thing you should try to keep at least some time for, \uline{~~16~~} yourwriting — and that's reading. Any writer needs to read as much and as widely as they can;it's the one \uline{~~17~~} supporter — Something you can't do without.


Time is finite. The older you yet, the \uline{~~18~~} it seems to go. We need to use it ascarefully and as \uline{~~19~~} as we can. That means prioritising out activities so that we spendmost time on the things we really want to do. If you are a writer, that means — \uline{~~20~~} —writing.