The outbreak of swine flu that was first detected in Mexico was declared a global epidemic on June 11, 2009. It is the first worldwide epidemic \uline{~~1~~} by the World Health Organization in 41 years.


The heightened alert \uline{~~2~~} an emergency meeting with flu experts in Geneva that assembled after a sharp rise in cases in Australia, and rising \uline{~~3~~} in Britain, Japan, Chile and elsewhere.


But the epidemic is `` \uline{~~4~~} '' in severity, according to Margaret Chan, the organization's director general, \uline{~~5~~} the overwhelming majority of patients experiencing only mild symptoms and a full recovery, often in the \uline{~~6~~} of any medical treatment.


The outbreak came to global \uline{~~7~~} in late April 2009, when Mexican authorities noted an unusually large number of hospitalizations and deaths \uline{~~8~~} healthy adults. As much of Mexico City shut down at the height of a panic, cases began to \uline{~~9~~} in New York City, the southwestern United States and around the world.


In the United States, new cases seemed to fade \uline{~~10~~} warmer weather arrived. But in late September 2009, officials reported there was \uline{~~11~~} flu activity in almost every state and that virtually all the \uline{~~12~~} tested are the new swine flu, also known as (A) H1N1, not seasonal flu. In the U.S., it has \uline{~~13~~} more than one million people, and caused more than 600 deaths and more than 6,000 hospitalizations.


Federal health officials \uline{~~14~~} Tamiflu for children from the national stockpile and began \uline{~~15~~} orders from the states for the new swine flu vaccine. The new vaccine, which is different from the annual flu vaccine, is \uline{~~16~~} ahead of expectations. More than three million doses were to be made available in early October 2009, though most of those \uline{~~17~~} doses were of the FluMist nasal spray type, which is not \uline{~~18~~} for pregnant women, people over 50 or those with breathing difficulties, heart disease or several other \uline{~~19~~} . But it was still possible to vaccinate people in other high-risk groups: health care workers, people \uline{~~20~~} infants and healthy young people.