Here's a common scenario that any number of entreprenuers face today:you're the CEO of a small business and though you're making a nice \uline{~~1~~} , you need to find a way to take it to the next level. what you need to do is \uline{~~2~~} growth by establishing a growth team. A growth team is made up of members from different departments within your company, and it harnesses the power of collaboration to focus \uline{~~3~~} on finding ways to grow.


Let's look at a real-world \uline{~~4~~} . Prior to forming a growth team, the software company BitTorrent had 50 employees. Working in the \uline{~~5~~} departments of engineering, marketing and product development. This brought them good results until 2012, when their growth plateaued. The \uline{~~6~~} was that too many customers were using the basic, free version of their product. And \uline{~~7~~} improvements to the premium, paid version, few people were making the upgrade.


Things changed, \uline{~~8~~} , when an innovative project marketing manager came aboard, \uline{~~9~~} a growth team and sparked the kind of \uline{~~10~~} perspective they needed. By looking at engineering issues from a marketing point of view, it became clear that the \uline{~~11~~} of upgrades wasn't due to a quality issue. Most customers were simply unaware of the premium version and what it offered.


Armed with this \uline{~~12~~} , the marketing and engineering teams joined forces to raise awareness by prominently \uline{~~13~~} the premium version to users of the free version. \uline{~~14~~} , upgrades skyrocketed, and revenue increased by 92 percent.


But in order for your growth, team to succeed, it needs to a have a strong leader. It needs someone who can \uline{~~15~~} the interdisciplinary team and keep them on course for improvement.


This leader will \uline{~~16~~} the target area, set clear goals and establish a time frame for the \uline{~~17~~} of these goals. This growth leader is also \uline{~~18~~} for keeping the team focus on moving forward and steer them clear of distractons. \uline{~~19~~} attractive, new ideas can be distracting, the team leader must recognize when these ideas don't \uline{~~20~~} the current goal and need to de put on the back burner.