As many people hit middle age, they often start to notice that their memory and mental clarity are not what they used to be. We suddenly can't remember \uline{~~1~~} we put the keys just a moment ago, or an old acquaintance's name, or the name of an old band we used to love. As the brain \uline{~~2~~}, we refer to these occurrences as ``senior moments.'' \uline{~~3~~} seemingly innocent, this loss of mental  focus can potentially have a(n) \uline{~~4~~} impact on our professional, social, and personal \uline{~~5~~}.


Neuroscientists, experts who study the nervous system, are increasingly showing that there's actually a lot that can be done. It \uline{~~6~~} out that the brain needs exercise in much the same way our muscles do, and the right mental \uline{~~7~~} can significantly improve our basic cognitive \uline{~~8~~}. Thinking is essentially a \uline{~~9~~} of making connections in the brain. To a certain extent, our ability to \uline{~~10~~} in making the connections that drive intelligence is inherited. \uline{~~11~~}, because these connections are made through effort and practice, scientists believe  that intelligence can expand  and fluctuate \uline{~~12~~} mental  effort.


Now, a new Web-based company has taken it a  step \uline{~~13~~} and developed the first ``brain training program'' designed to actually help people improve and regain their mental \uline{~~14~~}.


The Web-based  program \uline{~~15~~} you to systematically improve your  memory and attention skills. The program keeps \uline{~~16~~} of your progress and provides detailed feedback \uline{~~17~~} your performance and improvement. Most importantly, it \uline{~~18~~} modifies and enhances the games you play to \uline{~~19~~} on  the strengths you are developing – much like a(n) \uline{~~20~~} exercise routine requires you to increase resistance and vary your muscle use.