It is true that CEO pay has gone up—top ones may make 300 times the pay of typical workers on average, and since the mid-1970s, CEO pay for large publicly traded American corporations has, by varying estimates, gone up by about 500%. The typical CEO of a top American corporation now makes about \$18.9 million a year.


The best model for understanding the growth of CEO pay is that of limited CEO talent in a world where business opportunities for the top firms are growing rapidly. The efforts of America' s highest-earning 1% have been one of the more dynamic elements of the global economy. It's not popular to say. but one reason their pay has gone up so much is that CEOs really have upped their game relative to many other workers in the U.S. economy.


Today' s CEO, at least for major American firms, must have many mere skills than simply being able to ``run the company.'' CEOs must have a good sense of financial markets and maybe even how the company should trade in them. They also need better public relations skills than their predecessors, as the costs of even a minor slipup can be significant. Then there's the fact that large American companies are much more globalized than ever before, with supply chains spread across a larger number of countries. To lead in that system requires knowledge that is fairly mind-boggling. Plus, virtually all major American companies are becoming tech companies, one way or another. Beyond this, major CEOs still have to do all the day-to-day work they have always done.


The common idea that high CEO pay is mainly about ripping people off doesn't explain history very well. By most measures, corporate governance has become a lot tighter and more rigorous since the 1970s. Yet it is principally during this period of stronger governance that CEO pay has been high and rising. That suggests it is in the broader corporate interest to recruit top candidates for increasingly tough jobs.


Furthermore, the highest CEO salaries are paid to outside candidates, not to the cozy insider picks, another sign that high CEO pay is not some kind of depredation at the expense of the rest of the company. And the stock market reacts positively when companies tie CEO pay to, say, stock prices, a sign that those practices build up corporate value not just for the CEO.