Today we live in a world where GPS systems, digital maps, and other navigation apps are available on our smartphones. \uline{~~1~~} of us just walk straight into the woods without a phone. But phones \uline{~~2~~} on batteries, and batteries can die faster than we realize. \uline{~~3~~} you get lost without a phone or a compass, and you \uline{~~4~~} can't find north, we have a few tricks to help you navigate \uline{~~5~~} to civilization, one of which is to follow the land.


When you find yourself well \uline{~~6~~} a trail, but not in a completely \uline{~~7~~} area, you have to answer two questions: Which \uline{~~8~~} is downhill, in this particular area? And where is the nearest water source? Humans overwhelmingly live in valleys, and on supplies of fresh water. \uline{~~9~~}, if you head downhill, and follow any H2O you find, you should \uline{~~10~~} see signs of people.


If you've explored the area before, keep an eye out for familiar sights – you may be \uline{~~11~~} how quickly identifying a distinctive rock or tree can restore your bearings.


Another \uline{~~12~~} : Climb high and look for signs of human habitation. \uline{~~13~~}, even in dense forest, you should be able to \uline{~~14~~} gaps in the tree line due to roads,  train tracks,  and other paths  people carve \uline{~~15~~} the woods. Head toward these \uline{~~16~~} to find a way out. At night, scan the horizon for \uline{~~17~~} light sources, such as fires and streetlights, then walk toward the glow of light pollution.


\uline{~~18~~}, assuming you're lost in an area humans tend to frequent, look for the \uline{~~19~~} we leave on the landscape. Trail blazes, tire tracks, and other features  can \uline{~~20~~} you to civilization.