Being a good parent is, of course, what every parent would like to be. But defining what it means to be a good parent is undoubtedly very \uline{~~1~~} , particularly since children respond differently to the same style of parenting. A calm, rule-following child might respond better to a different sort of parenting than, \uline{~~2~~} , a younger sibling.


\uline{~~3~~} , there's another sort of parent that's a bit easier to \uline{~~4~~} : a patient parent. Children of every age benefit from patient parenting. Still, \uline{~~5~~} every parent would like to be patient, this is no easy \uline{~~6~~} . Sometimes parents get exhausted and frustrated and are unable to maintain a \uline{~~7~~} and composed style with their kids. I understand this.


You're only human, and sometimes your kids can \uline{~~8~~} you just a little too far. And then the \uline{~~9~~} happens: You lose your patience and either scream at your kids or say something that was a bit too \uline{~~10~~} and does nobody any good. You wish that you could \uline{~~11~~} the clock and start over, We've all been there.


\uline{~~12~~} , even though it's common, it's important to keep in mind that in a single moment of fatigue, you can say something to your child that you may \uline{~~13~~} for a long time. This may not only do damage to your relationship with your child but also \uline{~~14~~} your child's self-esteem.


If you consistently lose your \uline{~~15~~} with your kids, then you are inadvertently modeling a lack of emotional control for your kids. We are all becoming increasingly aware of the \uline{~~16~~} of modeling tolerance and patience for the younger generation. This is a skill that will help them all throughout life. In fact, the ability to emotionally regulate or maintain emotional control when \uline{~~17~~} by stress is one of the most important of all life's skills.


Certainly, it's incredibly \uline{~~18~~} to maintain patience at all times with your children. A more practical goal is to try, to the best of your ability, to be as tolerant and composed as you can when faced with \uline{~~19~~} situations involving your children. I can promise you this: As a result of working toward this goal. you and your children will benefit and \uline{~~20~~} from stressful moments feeling better physically and emotionally.