\item A lot of students take up law as their profession due to
\begin{tasks}
	\task the growing demand from clients.
	\task the increasing pressure of inflation.
	\task the prospect of working in big firms.
	\task the attraction of financial rewards.
\end{tasks}
\item Which of the following adds to the costs of legal education in most American states?
\begin{tasks}
	\task Higher tuition fees for undergraduate studies.
	\task Receiving training by professional associations.
	\task Admissions approval from the bar association.
	\task Pursuing a bachelor's degree in another major.
\end{tasks}
\item Hindrance to the reform of the legal system originates from
\begin{tasks}
	\task the rigid bodies governing the profession.
	\task lawyers' and clients' strong resistance.
	\task the stern exam for would-be lawyers.
	\task non-professionals' sharp criticism.
\end{tasks}
\item The guild-like ownership structure is considered ``restrictive'' partly because it
\begin{tasks}
	\task prevents lawyers from gaining due profits.
	\task bans outsiders' involvement in the profession.
	\task aggravates the ethical situation in the trade.
	\task keeps lawyers from holding law-firm shares.
\end{tasks}
\item In this text, the author mainly discusses
\begin{tasks}
	\task the factors that help make a successful lawyer in America.
	\task a problem in America's legal profession and solutions to it.
	\task the role of undergraduate studies in America's legal education.
	\task flawed ownership of America's law firms and its causes.
\end{tasks}