\item What is most wives' main expectation of their husbands?
\begin{tasks}
	\task Talking to them.
	\task Trusting them.
	\task Supporting their careers.
	\task Sharing housework.
\end{tasks}
\item Judging from the context, the phrase ``wreaking havoc'' (Line 3, Para. 2) most probably means \uline{~~~~}.
\begin{tasks}
	\task generating motivation
	\task exerting influence
	\task causing damage
	\task creating pressure
\end{tasks}
\item All of the following are true EXCEPT \uline{~~~~}.
\begin{tasks}
	\task men tend to talk more in public than women
	\task nearly 50 percent of recent divorces are caused by failed conversation
	\task women attach much importance to communication between couples
	\task a female tends to be more talkative at home than her spouse
\end{tasks}
\item Which of the following can best summarize the main idea of this text?
\begin{tasks}
	\task The moral decaying deserves more research by sociologists.
	\task Marriage break-up stems from sex inequalities.
	\task Husband and wife have different expectations from their marriage.
	\task Conversational patterns between man and wife are different.
\end{tasks}
\item In the following part immediately after this text, the author will most probably focus on \uline{~~~~}.
\begin{tasks}
	\task a vivid account of the new book Divorce Talk
	\task a detailed description of the stereotypical cartoon
	\task other possible reasons for a high divorce rate in the U.S.
	\task a brief introduction to the political scientist Andrew Hacker
\end{tasks}