People have speculated for centuries about a future without work. Today is no different, with academics, writers, and activists once again \uline{~~1~~} that technology is replacing human workers. Some imagine that the coming work-free world will be defined by \uline{~~2~~} : A few wealthy people will own all the capital, and the masses will struggle in an impoverished wasteland.


A different and not mutually exclusive \uline{~~3~~} holds that the future will be a wasteland of a different sort, one \uline{~~4~~} by purposelessness: Without jobs to give their lives \uline{~~5~~} , people will simply become lazy and depressed. \uline{~~6~~} , today's unemployed don't seem to be having a great time. One Gallup poll found that 20 percent of Americans who have been unemployed for at least a year report having depression, double the rate for \uline{~~7~~} Americans. Also, some research suggests that the \uline{~~8~~} for rising rates of mortality, mental-health problems, and addiction \uline{~~9~~} poorly-educated, middle-aged people is a shortage of well-paid jobs. Perhaps this is why many \uline{~~10~~} the agonizing dullness of a jobless future.


But it doesn't \uline{~~11~~} follow from findings like these that a world without work would be filled with unease. Such visions are based on the \uline{~~12~~} of being unemployed in a society built on the concept of employment. In the \uline{~~13~~} of work, a society designed with other ends in mind could \uline{~~14~~} strikingly different circumstances for the future of labor and leisure. Today, the \uline{~~15~~} of work may be a bit overblown. ``Many jobs are boring, degrading, unhealthy, and a waste of human potential,'' says John Danaher, a lecturer at the National University of Ireland in Galway.


These days, because leisure time is relatively \uline{~~16~~} for most workers, people use their free time to counterbalance the intellectual and emotional \uline{~~17~~} of their jobs. ``When I come home from a hard day's work, I often feel \uline{~~18~~} ,'' Danaher says, adding, ``In a world in which I don't have to work, I might feel rather different'' – perhaps different enough to throw himself \uline{~~19~~} a hobby or a passion project with the intensity usually reserved for \uline{~~20~~} matters.